%-------------------------
% Resume in LaTeX — Single Page
%-------------------------

\documentclass[11pt, a4paper]{article}

\usepackage{latexsym}
\usepackage[
    ignoreheadfoot,
    top=0.38in,
    bottom=0.38in,
    left=0.48in,
    right=0.48in
]{geometry}

\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage[charter]{mathdesign}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule\vspace{-4pt}]

%-------------------------
% Custom Commands
%-------------------------

\newcommand{\resumeItem}[1]{%
  \item\small{#1\vspace{-2pt}}%
}

\newcommand{\resumeSubheading}[4]{%
  \vspace{-2pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \hspace{4pt}\textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}%
}

\newcommand{\resumeProjectHeading}[2]{%
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small #1 & \textbf{\small #2}\\
  \end{tabular*}\vspace{-7pt}%
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------
\begin{document}

%----------HEADER----------
\begin{center}
    {\huge\textbf{KUMAR NAIDU KARRI}}\\[0.04in]
    \small
    \href{tel:+918500279547}{\underline{+91-8500279547}}
    \;\textbar\;
    \href{mailto:kumarnaidukarri22@gmail.com}{\underline{kumarnaidukarri22@gmail.com}}
    \;\textbar\;
    \href{https://www.linkedin.com/in/kumarnaidukarri}{\underline{LinkedIn}}
    \;\textbar\;
    \href{https://github.com/kumarnaidukarri}{\underline{GitHub}}
    \;\textbar\;
    \href{https://kumarnaidukarri.github.io/KumarPortfolio/}{\underline{Portfolio}}
    \;\textbar\;
    Hyderabad
\end{center}

\vspace{-10pt}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{Full Stack Developer with hands-on experience building MERN stack applications, REST APIs, and responsive web interfaces through professional roles and internships. Delivered features for ERP \& CRM platforms, developer matching applications, and vehicle booking systems — covering authentication, state management, real-time communication, and third-party integrations. Comfortable working across the full stack from React.js UI to Node.js/Express.js APIs and MongoDB.}

\vspace{-5pt}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
\vspace{0pt}
\resumeSubHeadingListStart

  \resumeSubheading
    {BiziQuick}{March 2026 -- May 2026}
    {Junior Software Developer}{Hyderabad, Telangana}
  \resumeItemListStart
    \resumeItem{Developed and maintained features for ERP \& CRM web platforms using React.js, Node.js, Express.js, and MongoDB.}
    \resumeItem{Built reusable React components and designed RESTful APIs handling full CRUD operations on the database.}
    \resumeItem{Integrated backend APIs with the frontend for a seamless user experience across business management modules.}
    \resumeItem{Participated in debugging, testing, and optimizing application performance.}
  \resumeItemListEnd

  \vspace{2pt}

  \resumeSubheading
    {GreyCat Digital and Revidd}{June 2025 -- Jan 2026}
    {Software Developer Intern}{Visakhapatnam, Andhra Pradesh}
  \resumeItemListStart
    \resumeItem{Developed and maintained scalable features for web applications using React.js.}
    \resumeItem{Debugged UI issues, logic errors, and dependency crashes to enhance application stability.}
    \resumeItem{Collaborated with cross-functional teams using React, Redux, REST APIs, Axios, Firebase, JavaScript, HTML5, and CSS3.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-7pt}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  % Project 0 — ERP & CRM
  \resumeProjectHeading
    {\textbf{ERP \& CRM Platform} $|$ \emph{Full Stack Web Application}}{}
  \resumeItemListStart
    \resumeItem{Developed and maintained modules including Client Management, Bill of Materials (BOM), Purchase Orders, Purchase Invoices, and Production Orders.}
    \resumeItem{Designed responsive UI components using React.js and implemented RESTful APIs with Node.js, Express.js, and MongoDB.}
    \resumeItem{Built end-to-end features covering CRUD operations, form validation, search, filtering, and pagination with seamless frontend-backend integration.}
    \resumeItem{\textbf{Tech Stack:} React.js, JavaScript, Node.js, Express.js, MongoDB, SASS, Material UI, REST APIs, Git}
  \resumeItemListEnd

  \vspace{-5pt}

  % Project 1 — DevTinder
  \resumeProjectHeading
    {\textbf{DevTinder} $|$ \emph{Full Stack Web Application}}%
    {\href{https://devtinder-frontend-teal.vercel.app/}{Live Demo}}
  \resumeItemListStart
    \resumeItem{Built a developer matching platform with authentication, profile management, and subscription-based access.}
    \resumeItem{Integrated real-time chat via Socket.io and Razorpay payment gateway; developed RESTful APIs with Node.js, Express.js, and MongoDB.}
    \resumeItem{Implemented JWT authentication and secure session handling using cookies and Bcrypt.}
    \resumeItem{\textbf{Tech Stack:} React, Redux, Node.js, Express.js, MongoDB, Tailwind, Socket.io, Razorpay, JWT, Bcrypt}
  \resumeItemListEnd

  \vspace{-5pt}

  % Project 2 — Car Rental
  \resumeProjectHeading
    {\textbf{Car Rental} $|$ \emph{Full Stack Web Application}}%
    {\href{https://car-rental-frontend-puce.vercel.app/}{Live Demo}}
  \resumeItemListStart
    \resumeItem{Built a vehicle booking platform with role-based access (Admin, Owner, User), secure JWT authentication, and backend validation.}
    \resumeItem{Developed RESTful backend services using Node.js and Express.js with MongoDB.}
    \resumeItem{Designed a responsive React.js interface for seamless user experience.}
    \resumeItem{\textbf{Tech Stack:} React, Node.js, Express.js, MongoDB, JWT, Bcrypt}
  \resumeItemListEnd

  \vspace{-5pt}

  % Project 3 — YouTube Clone
  \resumeProjectHeading
    {\textbf{YouTube Clone} $|$ \emph{Frontend Web Application}}%
    {\href{https://kumarprojects-namasteyoutubeapp.vercel.app/}{Live Demo}}
  \resumeItemListStart
    \resumeItem{Built a fully responsive YouTube clone with React and Tailwind CSS; integrated YouTube Data API for real-time video data.}
    \resumeItem{Implemented search with Google Suggestion API using debouncing and caching; managed global state with Redux Toolkit.}
    \resumeItem{Developed live chat via API polling, infinite nested comments, and applied \texttt{useMemo}/\texttt{useCallback}/\texttt{useRef} for rendering performance.}
    \resumeItem{\textbf{Tech Stack:} React.js, Redux Toolkit, Tailwind CSS, JavaScript (ES6+), React Router DOM, YouTube Data API}
  \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-9pt}

%-----------EDUCATION-----------
\section{Education}
\vspace{1pt}
\resumeSubHeadingListStart
  \resumeSubheading
    {Nadimpalli Satyanarayana Raju Institute of Technology}{2025}
    {\hspace{4pt}B.Tech in Computer Science and Engineering}{}
  \vspace{2pt}
  \resumeSubheading
    {Great Learning Academy / Udemy}{2025}
    {\hspace{4pt}MERN Stack Training}{}
\resumeSubHeadingListEnd

\vspace{-9pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\vspace{1pt}
\begin{itemize}[leftmargin=0.15in, itemsep=0pt, parsep=0pt]
  \item \small\textbf{Frontend:} HTML5, CSS3, SASS, Bootstrap, Tailwind CSS, DaisyUI, JavaScript (ES6+), React.js, Redux, Axios
  \item \small\textbf{Backend:} Node.js, Express.js, Python, Nginx, Firebase, Socket.io
  \item \small\textbf{Databases:} MongoDB, Mongoose, SQL, SQLite
  \item \small\textbf{Tools \& Platforms:} Git, GitHub, Linux, AWS, GCP, Vercel, Render, PM2, Postman, Jest, Prompt Engineering
  \item \small\textbf{Core Concepts:} OOP, RESTful APIs, WebSockets, JWT Authentication, Responsive Design, Operating Systems
\end{itemize}

\end{document}
